Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-17 analysis/paper/paper.Rmd
specify link function used, logit, in methods

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log pointwise predictive density via `loo_compare()`.

>>>>

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log pointwise predictive density via `loo_compare()`.
